An elaborate data set on human gait and the effect of mechanical perturbations

### 2015-03-17 paper.tex

In addition to the longitudinal perturbations, lateral perturbations were also
prescribed for a duration of four minutes in the pilot trials 3--8.
Figure~\ref{fig:lateral_perturbation} shows the effect of the lateral control
of the treadmill by plotting the commanded and measured treadmill positions.
These signals were generated in a similar manner using MATLAB and Simulink in
which a Gaussian white noise block that twice integrated to obtain the lateral
position. The signal was then high-pass filtered with a second-order
Butterworth filter to eliminate drift and then saturated so that the signal
remained within the 5~\si{\centi\meter} lateral range of the physical hardware.
The same perturbation signal was used for each of the three trials.
%
\begin{figure}
  \centering
  \includegraphics{figures/lateral_perturbation.pdf}
  \cprotect\caption{Commanded treadmill lateral deviation (red) and the
    recorded deviation (blue) for the trials 6, 7, and 8. Generated by
    \verb|src/lateral_perturbation_plot.m|.}
  \label{fig:lateral_perturbation}
\end{figure}

>>>>

In addition to the longitudinal perturbations, lateral perturbations were also
prescribed for a duration of four minutes in the pilot trials 3--8.
Figure~\ref{fig:lateral_perturbation} shows an example of the measured lateral
deviation of the treadmill base. These signals were generated in a similar
manner using MATLAB and Simulink in which a Gaussian white noise block was
twice integrated to obtain the lateral deviation. The signal was then high-pass
filtered with a second-order Butterworth filter to eliminate drift and then
saturated so that the signal remained within the 5~\si{\centi\meter} lateral
range of the physical hardware. The same perturbation signal was used for each
of the three trials.
%
\begin{figure}
  \centering
  \includegraphics{figures/lateral_perturbation.pdf}
  \cprotect\caption{The measured lateral deviation of the treadmill base from
    trial 6. Generated by \verb|src/lateral_perturbation_plot.m|.}
  \label{fig:lateral_perturbation}
\end{figure}
